Staged Abstract Interpreter

### 2018-02-01 paper/paper.tex
misc

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  It is well known that a staged interpreter is a compiler. A nature question is to ask 
  that what would be a staged abstract interpreter and how to obtain it in a mechanized 
  approach.

  In this paper, we systematically study the family of staged abstract interpreters, including 
  \citeauthor{Boucher:1996:ACN:647473.727587}'s Abstract Compilation, staged small-step 
  Abstracting Abstract Machines (AAM) and staged Abstracting Definitional Interpreters (ADI).
  To understand their relations, we firstly study the relations of their unstaged counterparts:
  we show how to obtain a abstracting definitional interpreter by a series of transformations
  from a small-step abstracting abstract machine. A key insight we show is how the pushdown 
  property of 
  analysis been obtained when transforming from small-step AAM to ADI, as well as how it 
  been lost in another direction.
  (TODO: pushdown for staged abstract interpreter?)

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  It is well known that a staged interpreter is a compiler. A nature question is to ask 
  that what would be a staged abstract interpreter and how to obtain it by a mechanized 
  approach.

  In this paper, we systematically study the family of staged abstract interpreters, including 
  \citeauthor{Boucher:1996:ACN:647473.727587}'s Abstract Compilation, staged small-step 
  Abstracting Abstract Machines (AAM) and staged Abstracting Definitional Interpreters (ADI).
  To understand their relations, we firstly study the relations of their unstaged counterparts:
  we show how to obtain a abstracting definitional interpreter by a series of transformations
  from a small-step abstracting abstract machine. A key insight we show is how the pushdown 
  control flow property of 
  analysis been obtained when transforming from small-step AAM to ADI, as well as how it 
  been lost in another direction.
  (TODO: pushdown for staged abstract interpreter?)
